Methods

### 2024-09-09 index.qmd
docs(book): updates to index, framework and protocol pages

* **Introduction** - background on the STARS project, pilot work, and the aim of work package 1
* **Methods** - summarises the methods which are described in detail in our protocol
* **Results** - describes the results of the reproductions and evaluations, and reflections from the process
* **Discussion** - considers and applies findings \

>>>>

* **Introduction** - background on STARS, pilot work, and the aim of work package 1
* **Methods** - summarises the methods which are described in detail in our protocol
* **Results** - describes the results of the reproductions and evaluations, and reflections from the process
* **Discussion** - considers and applies findings \

### 2024-09-09 pages/framework.qmd
docs(book): updates to index, framework and protocol pages

@@

>>>>

<!--TODO: Consider implications of:
* Reproduction
* Evaluation of the repository
* Evaluation of the article
* Timings -->

@@

**Interactive web app**: Could make a web app that serves as a "form" for people to complete and then downloaded their completed framework like there is set up for the [PRISMA checklist](https://prisma.shinyapps.io/checklist/).

## Reflections from the evaluations

<!-- TODO: Restructure this into implications for framework, and implications for STRESS-DES-->

**TBC - in progress below...**

Although we can comment on how commonly or uncommonly something met a criteria, it is only a small sample (n=6), so when covered in the DES best practice audit, that might be more informative, as baesd on far more studies.

From evaluation of repository:

* Open license - available on about half, added on request for rest, a very important one as without it you technically cannot reuse someones code
* Complete materials - rarely, so alot of time spent on writing code and figuring out how best to do that
* Dependency management - rarely done, and although not an issue in simpler cases, a big impact in more complex
* Model interface - provided for two although not helpful as (1) host no longer operating, and as not focus, didn't try to run locally, and (2) other app was viewable but didn't produce the figures and outcomes from paper (was more general, whilst paper delved into scenarios beyond app)

From evaluation of paper:

* It often took a long time (up to 2 hours). It would be valuable if the completed checklist were provided along with the paper, like how people often do with equator network reporting guidelines like PRISMA. Consider varying levels detail its possible to complete (yes/no, linking to sections, full detail). Linking to sections is minimum needed to be really useful. Yes/no doesn't impact time to find information really.
* Input parameters - very handy, as if uncertain in code, use this to check or code
* Some of my evaluations were more light handed (e.g. STRESS 1.2 and 1.3) whilst some were more nit-picky
* Run length - important for knowing when its slow
* Scenarios - important to be clear, felt provided in a table was the clearest

Reflections on STRESS-DES from having worked on it:

* 1.2 "how and when calculated" might feel like excess detail
* 1.3A providing name for each scenario doesn't always seem necessary
* 2.4 initially found confusing/irrelevant (e.g. "operation of conveyor")
* 3.2 would be helpful to have more examples
* 5.1 listing all packages and their versions is never particularly achievable or feasible. More feasible is specifying main package used for model (e.g. simmer, simpy, base R, numpy/pandas) and providing finer details in code (although it was helpful to have version of this package in the paper, when no versions were mentioned in the GitHub)
* 5.2 Algorithm used is tricky/uncommon knowledge
* 5.3 Event-processing machanism is tricky/uncommon knowledge
* Too many different things in several (could benefit from being clearer, seperated, or into components like 2.5). This was the case for 1.3, 3.3, 4.1, 4.3, 5.1, 5.2, 5.3, 5.4

Reflections from comparing what is in STRESS-DES v.s. ISPOR-derived:

* Scenarios - ISPOR has a simpler description
* Model uncertainities - nice that ISPOR requires this
* ISPOR has lots of items that relate to validity and how "good" it is (9 to 18) - whilst STRESS doesn't touch on this

### 2024-09-09 pages/protocol.qmd
docs(book): updates to index, framework and protocol pages

| Deviation | Description and reason for the change |
| --- | --- |
| Using the latest software packages | In the protocol, I had planned that - if no versions were provided  we select a version of the software and each package that is closest to but still prior to the date of the code archive or paper publication. I kept to this for the Python models (easily set using a conda/mamba environment). However, I had great difficulties attempting to do this in R, and could not successfully backdate both. As such, I used the latest versions of R and each package for those studies |
| Using percentage difference in results to help decided reproduction success | This is not particularly deviation, as I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g. both might be considered a small difference) depending on the scale used and what is being compared - whilst in another context with a different scale, 0.1 vs 0.2 might actually reflect a huge difference!). |
| Moving onto evaluation stage before receive author response regarding reproduction discrepancy | In the protocol, we required that authors are contacted if there are any remaining difficulties in running the code or items in the scope that were not reproduced. The authors were given a total of four weeks to respond if they chose to. We had implied that we must wait for this time to pass before continuing to the evaluation stage (since the three stages were presented as being completed one after another). The rationale for this was that the timings for the reproduction would be influenced by whether the evaluation had been completed or not, and vice versa. However, given the many possible influences on the timings, this was considered negligble. |
| Organisation of the repository for the research compendium | In the protocol, we had planned that seperate folders were created for data, methods and outputs. This was generally followed but, if an alternative structure seemed more suitable (for example, if the original study already divided items well, but perhaps with different folder names or with multiple scripts folders or so on, we might have used that original structure, as it still served the purpose of being clear and easy to re-run, whilst reducing the number of differences compared with the original study). |

>>>>

| Deviation | Description and reason for the change |
| --- | --- |
| Using the latest software packages | In the protocol, I had planned that - if no versions were provided  we select a version of the software and each package that is closest to but still prior to the date of the code archive or paper publication. I kept to this for the Python models (easily set using a conda/mamba environment). However, I had great difficulties attempting to do this in R, and could not successfully backdate both. As such, I used the latest versions of R and each package for those studies |
| Using percentage difference in results to help decided reproduction success | This is not particularly deviation, as I did explore this, but I ultimately found it very unhelpful, as the percentage difference could be greatly impacted by scale (for example, 0.1 vs 0.2 would appear much greater than 3 vs 4, but the actual meaning of these differences might be similar (e.g. both might be considered a small difference) depending on the scale used and what is being compared - whilst in another context with a different scale, 0.1 vs 0.2 might actually reflect a huge difference!). |
| Moving onto evaluation stage before receive author response regarding reproduction discrepancy or before getting consensus on reproduction | In the protocol, we required that authors are contacted if there are any remaining difficulties in running the code or items in the scope that were not reproduced. The authors were given a total of four weeks to respond if they chose to. We had implied that we must wait for this time to pass before continuing to the evaluation stage (since the three stages were presented as being completed one after another). The rationale for this was that the timings for the reproduction would be influenced by whether the evaluation had been completed or not, and vice versa. However, given the many possible influences on the timings, this was considered negligble.<br><br>We also required consensus on whether items had been succesfully reproduced or not before moving on. In two cases, this was not done due to a two week period of annual leave where it wouldn't be possible to get a second opinion, and so I progressed with the evaluation and got consensus on reproductions afterwards. |
| Organisation of the repository for the research compendium | In the protocol, we had planned that seperate folders were created for data, methods and outputs. This was generally followed but, if an alternative structure seemed more suitable (for example, if the original study already divided items well, but perhaps with different folder names or with multiple scripts folders or so on, we might have used that original structure, as it still served the purpose of being clear and easy to re-run, whilst reducing the number of differences compared with the original study). |
